A simple R markdown example

### 2020-05-20 R/rmarkdown.Rmd

---
output: pdf_document
fontsize: 9pt
geometry:
  - "landscape"
  - margin=0.5cm
  - paperwidth=5cm
  - paperheight=10cm
header-includes:
   - \usepackage[center,dvips,frame]{crop}
---

>>>>

---
output: pdf_document
fontsize: 9pt
geometry:
  - "landscape"
  - margin=0.5cm
  - paperwidth=6cm
  - paperheight=12cm
header-includes:
   - \usepackage[center,dvips,frame]{crop}
---
